---
title: "Portfolio 4 - Study 1 write-up"
author: "Adam"
date: "5/3/2022"
output: html_document
---

> The purpose of this portfolio is to have a singular write-up of what we found during Study 1 of my thesis.

## Set-up

```{r packages, echo=TRUE, message=FALSE}
library('psych')
library('readr')
library('reshape2')
library('dplyr')
library('lavaan')
library('Rcpp')
library('lme4')
library('lmerTest')
library('OpenMx')
library('semPlot')
library('tidyverse')
library('Hmisc')
```


#### Bringing in the data

```{r loading data, echo=TRUE, collapse=TRUE, message=FALSE}
study1 <- read_csv("data/Study1_data_R_cleaned.csv")

# Ensuring the dataframe is a tibble.
as_tibble(study1)

#Taking a look at the table.
View(study1)
```



## What was the goal of Study 1?

The purpose of the first study was to examine whether students’ disclosure in class settings is associated with their belonging. Additionally, I aimed to assess whether the prompting of disclosure by the instructor or by norms/routines in groups is positively associated with disclosure and belonging. 

While correlational, this study has the benefit of examining naturally occurring classes. As such, I expected a wide range in students’ experiences related to classroom-based disclosure. This diversity of class environments introduces noise but also increases generalizability. In the study, I sought to address three hypotheses:

HQ1: Students who report greater prompting of disclosure in class or groups will report greater actual disclosure in those classes or groups.

HQ2: Students who report greater disclosure in class or groups will report higher feelings of belonging in the class and at their institution.

HQ3: Students’ belonging in class will be positively correlated with their belonging at the institution. 



### What did I do?

I posted an advertisement on Prolific inviting college students who were currently taking one or more online courses to participate in an online survey about their experiences in online/blended classes. Students who agreed to participate were redirected to the Qualtrics survey platform. They were asked questions about their feelings of belonging at their institution overall. They were then asked to focus on one particular online class that they were currently taking (hereafter, the “target” class). If they were taking more than one online class, they were asked to focus on whichever class met earliest in the week. Next, they were asked questions about their feelings of belonging in the target class. Participants indicated whether they met in groups in the target class and, if so, they answered additional questions about their experiences in those groups.



### How did we analyze the data?

To assess if prompting disclosure predicted reported disclosure and reported disclosure predicted belonging, I conducted a path analysis. In addition to testing the direct effects pictured, I also tested indirect effects of prompting disclosure on belonging through actual disclosure for both the class and group levels. I included the following covariates: gender (dummy coded with female as the reference class), race (dummy coded with White as the reference class), number of classmates known prior to beginning the course, and number of group members known prior to beginning the course.


### What did I find?

#### Correlations

```{r bivariate correlations}
correlations <- study1 %>%
        select(class_belong_comp4, school_belong_comp4, class_disclose_comp2, group_disclose_comp2, cdiscl_prompt_comp2, gdiscl_prompt_comp2)

rcorr(as.matrix(correlations))
    
```


Everything except group prompted disclosure was correlated, which was not correlated with belonging at either level.

In response to H3, class and school belonging were correlated! To the best of my knowledge, this is the first study to show that they are correlated, but distinct, constructs. When considering belonging interventions, this has important ramifications- as we should consider whether we're influencing class or school belonging.

Class belonging and school belonging
  r=.54, p<.001



### Full Model

The first model combined class disclosure and group disclosure into a single model.

Model Test User Model:
                                                      
 Test statistic                               126.697
 
 Degrees of freedom                                35

 P-value (Chi-square)                           0.000

 Comparative Fit Index (CFI)                    0.669

 RMSEA                                          0.156

 SRMR                                           0.115

The fit is not very good for this model, which is a concern. 9941 bootstrap draws were completed before it terminated, so slightly less than 10,000.

Regressions:

                         Estimate  Std.Err  z-value  P(>|z|)

  Class belonging                                                       

Key variables

    Class disclosure        0.203    0.230    0.881    0.378

    Class prompted discl    0.191    0.189    1.010    0.313

    Group disclosure        0.082    0.195    0.419    0.675

    Group prompted discl   -0.065    0.213   -0.306    0.759
    
Others

    Asian                  -0.783    0.351   -2.232    0.026

    Classmates known        0.427    0.143    2.990    0.003   

 School belonging
 
Key variables

    Class disclosure       -0.161    0.188   -0.856    0.392
    
    Class prompted discl    0.232    0.165    1.403    0.161
    
    Group disclosure        0.241    0.151    1.597    0.110
    
    Group prompted discl   -0.136    0.192   -0.706    0.480  
    
Others

    Asian                  -0.676    0.306   -2.209    0.027  
    
    Classmates known        0.288    0.143    2.021    0.043    
 
 Covariances:
 
                                    Estimate  Std.Err  z-value  P(>|z|)

 Class and Group disclosure           0.549    0.115    4.777    0.000
                                                       
 Class and school belonging           0.487    0.086    5.650    0.000

Neither class disclosure nor group disclosure significantly predicted either class or institutional belonging. However, prompted disclosure in class was a significant predictor of class disclosure, and group prompted disclosure predicted group disclosure. 

Several of the covariates were also significant predictors of belonging. In particular, number of classmates known prior to the class significantly predicted both institutional belonging and class belonging. Asian students reported significantly lower class and institutional belonging than White students. Of note, none of the Asian students in my sample were international students.

The covariance between class disclosure and group disclosure was very high, which suggests that there may be substantial collinearity between the two variables. Because of this, I decided to conduct path analyses separately for the class and group disclosure variables.



### Class only model

Model Test User Model:
                                                      
 Test statistic                                 11.453

  Degrees of freedom                                7

  P-value (Chi-square)                          0.120

 Comparative Fit Index (CFI)                    0.982
 
 RMSEA                                          0.046
 
 SRMR                                           0.021

This model is a much better fit for the data.

10,000 bootstrap draws completed

Regressions:

                         Estimate  Std.Err  z-value  P(>|z|)

  Class belonging    
  
Key variables

    Class disclosure        0.341    0.102    3.329    0.001
    
    Class prompted discl    0.102    0.099    1.034    0.301

Others

    Asian                  -0.386    0.231   -1.674    0.094
    
    Nonbinary		           -0.829    0.273   -3.034    0.002
    
    Classmates known        0.127    0.064    1.978    0.048   

 School belonging 

Key variables

    Class disclosure        0.124    0.097    1.278    0.201
    
    Class prompted discl    0.071    0.082    0.861    0.389

Others 

    Asian                  -0.388    0.203   -1.906    0.057  
    
    Classmates known        0.288    0.143    2.021    0.043    
 

Indirect effects

    total_class      	      0.260    0.081    3.226    0.001
    
    total_school            0.228    0.080    2.855    0.004

Class disclosure significantly predicts class belonging, Asian was marginal at both levels, and non-binary appears as a significant predictor. Once more, classmates known is a significant predictor of at both levels.

The indirect effects were significant for the effect of class prompted disclosure on belonging through actual class disclosure, suggesting that although the main effect is not significant the effect of prompted disclosure on belonging is mediated by class disclosure.

The result here is that class disclosure is predicting class belonging, which is partial support for the model that I propose!


### Group model

 Model Test User Model:
                                                      
 Test statistic                                 6.880
 
 Degrees of freedom                                 8

 P-value (Chi-square)                           0.550

 Comparative Fit Index (CFI)                    1.000

  RMSEA                                          0.000

  SRMR                                           0.027

9949 bootstrap draws were performed.

Regressions:

                         Estimate  Std.Err  z-value  P(>|z|)

  Class belonging

Key variables

    Group disclosure        0.224    0.131    1.717    0.086 

    Group prompted discl    0.098    0.157    0.625    0.532

Others

    Asian                   0.829    0.351   -2.361    0.018

    Classmates known        0.445    0.135    3.304    0.001  

    Group known            -0.229    0.122   -1.881    0.060  
  
  School belonging                                                      

    Group disclosure        0.153    0.114    1.341    0.180

    Group prompted discl    0.030    0.147    0.204    0.839 

Others

    Asian	           -0.691    0.301   -2.295    0.022

    Classmates known        0.271    0.136    1.992    0.046

 MEDIATION

    Group disclosure                                                     

    Group prompted discl    0.427    0.127    3.358    0.001

     total_class            0.523    0.162    3.226    0.001

     total_group            0.126    0.142    0.885    0.376 

Similar to the full model, prompted disclosure in groups was a significant predictor of group disclosure. Group disclosure was not a significant predictor of either institutional belonging or class belonging. The direct effect of group prompted disclosure on belonging was nonsignificant, though the indirect effect was significant for class belonging but nonsignificant for institutional belonging. Similar to class belonging, the significant indirect effect is due to the correlation between group prompted disclosure and actual disclosure, and the inclusion of additional significant predictors in the model.

As in both previous models, Asian students reported significantly lower belonging in class and at their institution, and number of classmates known prior was a significant positive predictor of belonging at the class and institutional levels. 

In this model, number of group members known prior was also a significant predictor of class belonging.


### Problems with the study

One of the major issues is that we lost a lot of power including groups- but this also underscores the importance of disclosure interventions. According to the study, nearly half of participants don't use groups in their online classes, and two-thirds reported no or almost no disclosure!

If we find that disclosure can play an important role in promoting belonging, then this absence could be very problematic. Looking forward, that's what we hope to test in Study 2.

